---
title: "An Rmarkdown Template"
author: A Name
date: Fall 2015
output: pdf_document
---

We can use markdown text here. You can make text *italic* and
**bold**. Rmarkdown does not care about spacing between words of after
sentences.                  See? This looks just       fine when you
output a PDF document.

New paragraphs require an empty line. In order to output a pdf
document, you need to install the `rmarkdown` package in R.

```{r, eval=FALSE}
install.packages("rmarkdown")
```

Once you've done that, you can turn the .Rmd document into a pdf file
with the following command in R:

```{r, eval=FALSE}
rmarkdown::render("your-document-name.Rmd")
```

If you're using RStudio, you can click the "knit" button, which
accomplishes the same thing. Note that you will need \LaTeX~ installed
in order to make a pdf.

Once we've done that, you can use rmarkdown to include R code easily
in your problem sets: 

```{r}
x <- 1:1570

mean(x)
```

These r "chunks" can take options. So, for example, because I didn't
want to evaluate the installation or render chunks above, I added
`eval=FALSE` to those options.

We can also take advantage of \LaTeX 's "math mode." For example,
inline math can be included between two dollar signs $x=3$ like
this. Or we can use display math between double dollar signs:

$$\bar{x} = \dfrac{1}{n} \sum_{i=1}^n x_i$$

You can find much more information about how all of this works on
rmarkdown's website [here](http://rmarkdown.rstudio.com/)
